\documentclass[12pt]{article}
\usepackage{setspace}
\date{Septemeber 13, 2018}
\title{Artificial Intelligence PS0c}
\author{Rushabh Doshi}
\usepackage[margin=1.5in]{geometry}

\begin{document}
\maketitle
\doublespace
This agent is in the computer science office 4th floor, room 405 in Dan hall, but it can be commonly found anywhere in any room, and is found almost everywhere. This single agent is responsible for illuminating the environment through motion detection in its environment. The environment in room 405, is an office room like every other, a door which you enter, help desk on your left entree, and two rooms in the back where other people work. When someone enters the room, it is the job of this agent to track and detect the motion to function. The agent obviously has a sensor that detects motion in its environment and react, this means the environment has to be fully observable by the agent, which it is. Given this information, this agent would be categorized in the group of simple-reflex agent, and none other. Simple agents are responsible for simple things like select actions on the basis of the current precepts, ignoring the rest of the precept history. This agent's decision is only based on the present time, not future or past. A simple function this agent would have would be that if it detects motion in the current time, illuminate the lights by means of letting electricity through for 15 minutes, and then it will automatically turn off. In between the time it reads motion to turn the light off and the time the lights automatically turn off, the agent is continuing to read any motion and "reset" the countdown for when the lights turn off. With no information regarding the past or the future, this agent acts in the present moment, thus being categorized with the simple-reflex agents, and not the other complex agents, which is probably not required for this type of utility. 
\end{document}